### 2013-09-25 latex/paper-PLOS_ONE-revised.tex
Final edits before resubmission.

As the number of empirically determined 3D protein crystal structures has grown over the years, it has become apparent that neither the Rose~\cite{Rose1985} nor the Miller~\cite{Miller1987} scale accurately identifies the true upper bound for a residue's ASA. In fact, virtually all amino acids display, on occasion, ASA values in excess of the normalization ASA values provided by either scale. Some do so quite frequently (e.g.\ R, D, G, K, P), reaching RSA values of up to 1.2. This discrepancy, which leads to RSA values $>1$, is generally known in the field though rarely acknowledged in print. A recent study carried out an extensive empirical survey of ASA values in PDB structures and found that the most accessible conformations are generally found in loops and turns, not in the extended conformation \cite{SinghAhmad2009}. The authors of that study suggested to use conformation-dependent maximum ASA values for normalization \cite{SinghAhmad2009}.

>>>>

As the number of empirically determined 3D protein crystal structures has grown over the years, it has become apparent that neither the Rose~\cite{Rose1985} nor the Miller~\cite{Miller1987} scale accurately identifies the true upper bound for a residue's ASA. In fact, virtually all amino acids display, on occasion, ASA values in excess of the normalization ASA values provided by either scale. Some do so quite frequently (e.g.\ R, D, G, K, P), reaching RSA values of up to 1.2. This discrepancy, which leads to RSA values $>1$, is generally known in the field though rarely acknowledged in print. One exception is a recent study that carried out an extensive empirical survey of ASA values in PDB structures  \cite{SinghAhmad2009}. That study found that the most accessible conformations are generally found in loops and turns, not in the extended conformation, and it suggested to use conformation-dependent maximum ASA values for normalization \cite{SinghAhmad2009}.
